Theories of deliberated choice

### 2023-06-18 simple.tex
Corr: infinite claim is NOT fals
Anonymity

We now say that $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
$\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is falsifiable.
	Consider any ${\allleadstog} \notin C$, thus satisfying $\exists k \suchthat (\ar)^k \nileadstog \phi$. Consider $O = \set{(i, (\ar)^k, {\allleadstog}(i, (\ar)^k) ≠ \phi)}$, thus with $O \subset {\allleadstog}$. We have $S_O \cap C = \emptyset$: consider any $O \subset f$, it is not in $C$.
\end{example}
\begin{example}
	\label{ex:unfals}
	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
	Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any ${\allleadstog'}$ such that $O \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
	Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
	\Cref{ex:unfals} concludes.
\end{example}
\begin{example}
	Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
	Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $O = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}

@@

$C$ is \emph{suitable} iff it holds and is informative and falsifiable.
\begin{example}[To be corrected]
	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
	Then $\forall i: \ar \ileadstostg \phi$ is suitable.

	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
\end{example}

>>>>

We now say that $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
$\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$. Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	\label{ex:unfals}
	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
	Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any ${\allleadstog'}$ such that $O \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
	Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
	\Cref{ex:unfals} concludes.
\end{example}
\begin{example}
	Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
	Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $O = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}

@@

Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
(TODO Alt: very strong, $\forall \allleadsto \in C, i, j \in I: \ileadsto = \jleadsto$; misses for example $\card{\set{i \suchthat \hist \ileadsto \phi}} = \frac{I}{2}$; strong: $\set{\ileadsto \suchthat \allleadsto \in C} = \set{\jleadsto \suchthat \allleadsto \in C}$; misses perhaps “if $i$ says… then $j$ says…”.)
\begin{example}
	Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$. Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
\end{example}

$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
\begin{example}
	Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
	Then $\forall i: \ar \ileadstostg \phi$ is suitable.
	Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
\end{example}
